A Regularized Time Varying Vector Error Correction Model

### 2017-05-10 articles-conferences/elsevier-2016/src/background.tex
elsevier

Fit the model to the data y1,…,yt and let y^t+1 denote the forecast of the next observation. Then compute the error (et+1∗=yt+1−y^t+1) for the forecast observation.
Repeat step 1 for t=m,…,n−1 where m is the minimum number of observations needed for fitting the model.
Compute the MSE from em+1∗,…,en∗.
References

>>>>

Fit the model to the data $y1,…,yt$ and let $y^t+1$ denote the forecast of the next observation. Then compute the error ($et+1∗=yt+1−y^t+1$) for the forecast observation.
Repeat step 1 for t=m,…,n−1 where m is the minimum number of observations needed for fitting the model.
Compute the MSE from $em+1∗,…,en∗$.
References
